Supplementary information for ``CLM5-PPE"

### 2024-08-06 ms/supp.tex
overleaf
supp info extended

\begin{landscape}
\begin{figure}[h]
\centering
\includegraphics[width=50pc]{figs/supp/survivability.png}
\caption{PFT survivability across the six ensembles. The sixteen natural vegetation PFTs are on the vertical axis, and the perturbation number sets the horizontal axis. A PFT is classified as dead in a given gridcell if it does not achieve an LAI of at least 0.1 m2/m2 at any point during the simulation. A PFT is classified as dead for a given perturbation if more than 50\% of the area that was alive with the default parameters is dead in the perturbed simulation.}
\label{supp:surv}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=60pc]{figs/supp/ilamb_lines.png}
\caption{The convergence of several scoring metrics with increasing sparsegrid resolution across a variety of CLM variables. All scores tend towards 1 as the number of sparsegrid clusters (k) approaches the 5666 gridcells for the native resolution of our 2-degree simulations. }
\label{supp:ilamb}
\end{figure}
\end{landscape}

@@

>>>>

\begin{landscape}
\begin{figure}[h]
\centering
\includegraphics[width=50pc]{figs/supp/survivability.png}
\caption{PFT survivability across the six ensembles. The sixteen natural vegetation PFTs are on the vertical axis, and the perturbation number sets the horizontal axis. A PFT is classified as dead in a given gridcell if it does not achieve an LAI of at least 0.1 m2/m2 at any point during the simulation. A PFT is classified as dead for a given perturbation if more than 50\% of the area that was alive with the default parameters is dead in the perturbed simulation.}
\label{supp:surv}
\end{figure}
\end{landscape}

\begin{figure}[h]
\centering
\includegraphics[width=40pc]{figs/supp/biome_tp.png}
\caption{Each of the 400 sparse gridcells plotted according to their Whittaker biomes}
\label{supp:whit1}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=40pc]{figs/supp/biome_latlon.png}
\caption{Cartesian plot of the 400 sparse gridcells labeled by their Whittaker biomes}
\label{supp:whit2}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=23pc]{figs/supp/biome_areas.png}
\caption{Total represented land area associated with each of the ten Whittaker biomes utilizing the CLM5.1 sparse grid}
\label{supp:whit3}
\end{figure}

\begin{landscape}
\begin{figure}[h]
\centering
\includegraphics[width=60pc]{figs/supp/ilamb_lines.png}
\caption{The convergence of several scoring metrics with increasing sparsegrid resolution across a variety of CLM variables. All scores tend towards 1 as the number of sparsegrid clusters (k) approaches the 5666 gridcells for the native resolution of our 2-degree simulations. }
\label{supp:ilamb}
\end{figure}
\end{landscape}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figs/supp/anomaly_errors.png}
\caption{buggy climate forcing}
\label{supp:abug}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=30pc]{figs/supp/AF2095_rankings.png}
\caption{buggy climate forcing}
\label{supp:abug}
\end{figure}
